{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-07-02 thesis/education.tex
reorganize education eval/bias/retro and setup eval Qs

\subsection{Evaluation}

% TODO FIXME
Landslide is great and should be used in 410. Dave wants to use it. That's enough evidence right there.

@@

\subsection{Evaluation}

% survey questions i WISH i had asked
% - did you have any technical difficulties w landslide that i had to intervene on
% mb anything else from timmys 2nd latest email

@@

@@

% \section{Survey results} % ???

>>>>

@@

\section{Evaluation}

I pose the following evaluation questions.

\begin{itemize}
	\item How many bugs, and of what severities, does Landslide help students find and fix before submitting their code?
	\item Does Landslide use result in higher quality submissions, whether directly for P2, or for subsequent projects as well?
	\item Do students feel the experience is worthwhile, as compared to stress testing?
	\item How well does Landslide apply to operating systems projects outside of CMU?
\end{itemize}
\vspace{1em}

The data set is comprised of Landslide's automatically-generated usage snapshots
from CMU students from semesters Spring 2015 to Spring 2018 inclusive,
% and PSU \psuos from Spring 2018, % no snapshots from psu
CMU's official project grades from same,
CMU students' survey responses and submitted project code from Fall 2017 and Spring 2018
PSU students' survey responses and submitted project code from Spring 2018,
and U. Chicago students' survey responses from Fall 2017.

\subsection{Bug-finding}

\subsection{Student submission quality}

\subsection{Student opinions}

\subsection{Other universities}

\section{Discussion}

\subsection{Bias}

%%%% pintos %%%%
% survey questions i WISH i had asked
% - did you have any technical difficulties w landslide that i had to intervene on
% mb anything else from timmys 2nd latest email

Human subjects research is inherently messy.
More than just drawing firm conclusions from
the opinions of students who are just learning concurrency to begin with,
student feedback in turn guided the constant development
of Landslide, and the experimental design itself,
as the semesters went by.
In this section I will fantasize about how I might have run more perfect experiments
granted the impossible wish of knowing then what I know now.

\subsubsection{Pebbles}

@@

\subsubsection{Pintos}

@@
